---
title: "Eating Out"
author: "Tiffany Alvarado"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r, eat, setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out. The variable name you are looking for is "eatout".
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r,datadata, include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(haven)
require(knitr)
require(foreign)
library(haven)
library(plyr)
```

```{r,data,eat.rmd,eval=FALSE}
GSS <-read_dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```



# Methods
RACE IS CAT  

EATING OUT IS CAT  

SO WE USE THE CAT ~ CAT HELPER FILE  


```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```
The races are white, black and other. The blue represents ate out last week, the orange represents who did not eat out. White people eat out the most rather than black and other.

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

The numerical results show that the white people which is 83.11% eat out more a week then the 69.04% that don't. 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=T)
```
The chi score shows the p-value is 0.00002, therefor we reject the null hypothesis that there is no variance between the races. 

The fisher test shows the p-value is 0.593 so we fail to reject the null hypothesis meaning there IS a difference between the white and black races while eating out. There is no evidence between a difference with the black and white races. 

